On exponential sums arising from the classical doubling method

### 2025-04-11 main.tex
Parenthesis

        \item (Types B,C,D Case 1) $w$ is conjugate to a cycle of length $n$. \calvin{Add in note about the two type B cases. Maybe really should just talk about $\Frobenius$ action} In this case $\algebraicGroup{T} = \restrictionOfScalars{\finiteFieldExtension{n}}{\finiteField}{\multiplcativeScheme}$ with $\Frobenius$ acting by $w$ on the domain and by the cycle $(w,w_n w w_n)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\multiplicativegroup{\finiteFieldExtension{n}},\alpha}).$$

@@

 In this case $\algebraicGroup{T} = \restrictionOfScalars{\finiteFieldExtension{n}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}$ with $\Frobenius$ acting by $w$ on the domain and by a cycle of length $2n$ on the image, and $$x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n}).$

@@

		$$x_{\multiplicativegroup{\finiteFieldExtension{n}} \times \multiplicativegroup{\finiteFieldExtension{n}},\alpha \times \alpha^{-q}} = \phi(x_{\multiplicativegroup{\finiteFieldExtension{n}},\alpha}).$$

@@

        \end{smallmatrix}\right)$ on the image, and $$x_{\multiplicativegroup{\finiteFieldExtension{2n}},\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n})$

>>>>

        \item (Types B,C,D Case 1) $w$ is conjugate to a cycle of length $n$. \calvin{Add in note about the two type B cases. Maybe really should just talk about $\Frobenius$ action} In this case $\algebraicGroup{T} = \restrictionOfScalars{\finiteFieldExtension{n}}{\finiteField}{\multiplcativeScheme}$ with $\Frobenius$ acting by $w$ on the domain and by the cycle $(w,w_n w w_n)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi\left(x_{\multiplicativegroup{\finiteFieldExtension{n}},\alpha}\right).$$

@@

 In this case $\algebraicGroup{T} = \restrictionOfScalars{\finiteFieldExtension{n}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}$ with $\Frobenius$ acting by $w$ on the domain and by a cycle of length $2n$ on the image, and $$x_{\finiteField_{2n}^\times,\theta'}=\phi \left(x_{\NormOneGroup{2n},\theta}\right)$$ where $\theta'\left(t\right) = \theta\left(t^{1-q^n}\right).$

@@

		$$x_{\multiplicativegroup{\finiteFieldExtension{n}} \times \multiplicativegroup{\finiteFieldExtension{n}},\alpha \times \alpha^{-q}} = \phi\left(x_{\multiplicativegroup{\finiteFieldExtension{n}},\alpha}\right).$$

@@

        \end{smallmatrix}\right)$ on the image, and $$x_{\multiplicativegroup{\finiteFieldExtension{2n}},\theta'}=\phi\left(x_{\NormOneGroup{2n},\theta}\right)$$ where $\theta'\left(t\right) = \theta\left(t^{1-q^n}\right)$.
